Case Study: ChIP-seq Differential Peak Calling (pre-defined regions)

### 2018-03-13 datasets/ChIP-seq/ChIPseq-promoters.Rmd

```{r count, results='hide', message=FALSE, warning=FALSE}
if (file.exists(result_file)) {
    load(result_file)
} else {
    dds <- DESeqDataSetFromMatrix(countData = rc,
                                  colData = as.data.frame(meta),
                                  design = ~ lab + cellline)
    dds <- DESeq(dds, fitType = "mean")
    dat <- as.data.frame(results(dds))
    colnames(dat) <- c('ind_covariate', 'effect_size', 'SE',
                       'stat', 'pval', 'padj')
    ## compute test-statistic from p-value for ASH
    dat <- dplyr::mutate(dat,
                         test_statistic = qnorm(exp(log(pval)-log(2)),
                                                lower.tail=FALSE),
                         test_statistic = test_statistic * sign(effect_size))
    ## remove regions with effect sizes = NA
    dat <- dat[!is.na(dat$effect_size), ]
    save(dat, file = result_file)
}
```

>>>>

```{r count, results='hide', message=FALSE, warning=FALSE}
if (file.exists(result_file)) {
    load(result_file)
} else {
    dds <- DESeqDataSetFromMatrix(countData = rc,
                                  colData = as.data.frame(meta),
                                  design = ~ lab + cellline)
    dds <- DESeq(dds, fitType = "mean")
    dat <- as.data.frame(results(dds, independentFiltering  = FALSE))
    colnames(dat) <- c('ind_covariate', 'effect_size', 'SE',
                       'stat', 'pval', 'padj')
    ## compute test-statistic from p-value for ASH
    dat <- dplyr::mutate(dat,
                         test_statistic = qnorm(exp(log(pval)-log(2)),
                                                lower.tail=FALSE),
                         test_statistic = test_statistic * sign(effect_size))
    ## remove regions with effect sizes = NA
    dat <- dat[!is.na(dat$effect_size), ]
    save(dat, file = result_file)
}
```
